---
title: "Cyclone Ocean Waves – Daily hazard maps"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
params:
  outdir: "outputs/latest"
  max_storms: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

suppressPackageStartupMessages({
  library(terra)
  library(leaflet)
  library(leafem)
})
```

This page reads the most recent outputs in `r params$outdir` and builds interactive maps for each in-force system.

```{r load-index}
outdir <- params$outdir
idx_file <- file.path(outdir, "index.csv")
stopifnot(file.exists(idx_file))

idx <- read.csv(idx_file, stringsAsFactors = FALSE)

# Keep successful rows and limit for page size
idx <- idx[idx$status == "ok", , drop = FALSE]
idx <- head(idx, params$max_storms)

if (nrow(idx) == 0) {
  stop("No successful storms found in index.csv")
}

idx
```

## Storm maps {.tabset}

```{r maps, results='asis'}
to_wgs84 <- function(x) {
  # Leaflet expects WGS84 (EPSG:4326)
  if (is.null(crs(x))) return(x)
  try(terra::project(x, "EPSG:4326"), silent = TRUE)
}

make_pal <- function(r) {
  rng <- terra::minmax(r)
  leaflet::colorNumeric("viridis", domain = c(rng[1,1], rng[2,1]), na.color = "transparent")
}

for (k in seq_len(nrow(idx))) {
  row <- idx[k, ]

  cat("\n\n### ", row$name, " (", row$TCid, ")\n\n", sep = "")

  # Track / forecast vector
  TC <- terra::vect(row$gpkg)

  # Full hazard rasters (multi-layer)
  hs0 <- if (!is.na(row$haz_hs0_tif) && file.exists(row$haz_hs0_tif)) terra::rast(row$haz_hs0_tif) else NULL
  pr  <- if (!is.na(row$haz_pr_tif)  && file.exists(row$haz_pr_tif))  terra::rast(row$haz_pr_tif)  else NULL

  if (is.null(hs0) || is.null(pr)) {
    cat("*Hazard rasters not found for this storm (expected haz_Hs0_***.tif and haz_Pr_***.tif).* \n\n")
    next
  }

  # Choose layers: peak Hs0 time, min pressure time (from index if available; otherwise compute)
  hs0_names <- names(hs0)
  pr_names  <- names(pr)

  hs0_peak_i <- if (!is.na(row$hs0_peak_time)) match(row$hs0_peak_time, hs0_names) else NA_integer_
  pr_min_i   <- if (!is.na(row$pr_min_time))   match(row$pr_min_time,  pr_names)  else NA_integer_

  if (is.na(hs0_peak_i)) {
    hs0_by_t <- as.numeric(terra::global(hs0, "max", na.rm = TRUE)[,1])
    hs0_peak_i <- if (all(is.na(hs0_by_t))) 1 else which.max(hs0_by_t)
  }
  if (is.na(pr_min_i)) {
    pr_by_t <- as.numeric(terra::global(pr, "min", na.rm = TRUE)[,1])
    pr_min_i <- if (all(is.na(pr_by_t))) 1 else which.min(pr_by_t)
  }

  hs0_peak <- hs0[[hs0_peak_i]]
  pr_min   <- pr[[pr_min_i]]

  hs0_max  <- terra::app(hs0, fun = max, na.rm = TRUE)
  pr_min_s <- terra::app(pr,  fun = min, na.rm = TRUE)

  # Project to EPSG:4326 for Leaflet
  TC_ll      <- to_wgs84(TC)
  hs0_peak_ll <- to_wgs84(hs0_peak)
  hs0_max_ll  <- to_wgs84(hs0_max)
  pr_min_ll   <- to_wgs84(pr_min)
  pr_min_s_ll <- to_wgs84(pr_min_s)

  # Palettes
  pal_hs0p <- make_pal(hs0_peak_ll)
  pal_hs0m <- make_pal(hs0_max_ll)
  pal_prp  <- make_pal(pr_min_ll)
  pal_prm  <- make_pal(pr_min_s_ll)

  # Create map
  m <- leaflet() |>
    addProviderTiles("CartoDB.Positron") |>
    addScaleBar(position = "bottomleft") |>
    addPolylines(
      data = TC_ll[TC_ll$DATASET == "track", ],
      weight = 3, opacity = 0.9,
      group = "Track (observed)"
    ) |>
    addPolylines(
      data = TC_ll[TC_ll$DATASET == "forecast", ],
      weight = 3, opacity = 0.8, dashArray = "6,6",
      group = "Track (forecast)"
    ) |>
    leafem::addRasterImage(
      hs0_peak_ll, opacity = 0.65,
      colors = pal_hs0p, group = paste0("Hs0 @ peak (", names(hs0)[hs0_peak_i], ")")
    ) |>
    leafem::addRasterImage(
      hs0_max_ll, opacity = 0.65,
      colors = pal_hs0m, group = "Hs0 max (over time)"
    ) |>
    leafem::addRasterImage(
      pr_min_ll, opacity = 0.65,
      colors = pal_prp, group = paste0("Pressure @ min (", names(pr)[pr_min_i], ")")
    ) |>
    leafem::addRasterImage(
      pr_min_s_ll, opacity = 0.65,
      colors = pal_prm, group = "Pressure min (over time)"
    ) |>
    addLayersControl(
      overlayGroups = c(
        "Track (observed)", "Track (forecast)",
        paste0("Hs0 @ peak (", names(hs0)[hs0_peak_i], ")"),
        "Hs0 max (over time)",
        paste0("Pressure @ min (", names(pr)[pr_min_i], ")"),
        "Pressure min (over time)"
      ),
      options = layersControlOptions(collapsed = FALSE)
    )

  print(m)

  cat("\n\n")
}
```

### Notes

- This report shows four raster layers per storm: **Hs0 at peak time**, **Hs0 max over time**, **pressure at minimum time**, and **pressure min over time**.
- The full multi-layer hazard rasters are saved as GeoTIFFs (e.g. `haz_Hs0_001.tif`, `haz_Pr_001.tif`) and can be inspected directly with `terra::rast()`.
